Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
Styling equations

  Now we estimate the cost of $\OPT(\sigma_E)$ by accounting savings from migrations.
  By performing a swap of nodes $(u,v)$, $\OPT$ collocates $u$ with two nodes $u', u''$, and $v$ with two nodes $v'$, $v''$.
  This may allow to serve requests between $(u,u')$, $(u,u'')$, $(v,v')$ and $(v,v'')$ for free afterwards.
  As $\sigma_E$ consists of requests to unsaturated pairs, and it accounts only for external requests, there are at most $\alpha-1$ requests between each of these pairs.
  By performing a single migration that costs $\alpha$, $\OPT$ may avoid paying the remote serving costs for at most $4\cdot (\alpha - 1)$ requests from $\sigma_E$.
  Thus, for serving $\sigma_E$, $\OPT$ pays at least $W \cdot \frac{\alpha}{4\cdot (\alpha-1)}$.
  This gives us
  \begin{equation*}
    \OPT(\sigma_E) + \OPT(M)  \geq (|\sigma_E|-3\cdot\ell\cdot(\alpha - 1)) \cdot \frac{\alpha}{4\cdot (\alpha-1)}
    \geq |\sigma_E| / 4 - 4\cdot \ell \cdot \alpha.
  \end{equation*}
  From that, we obtain $|\sigma_E| \geq 4\cdot(\OPT(\sigma_E)+\OPT(M)) + 16\ell \cdot \alpha$.
  Let $E := \OPT(\sigma_E) + \OPT(M)$. Finally, we are ready to bound the competitive ratio
  \begin{equation*}
    \frac{\TAlg(\sigma)}{\OPT(\sigma)} \leq \frac{10\alpha \cdot \ell + |\sigma_E|}{(\alpha + \OPT(\sigma_E) + \OPT(M))/2} \leq \frac{52\alpha\cdot\ell + 8\cdot E}{\alpha + E} \leq 52 \ell = O(\ell).
  \end{equation*}

>>>>

  Now we estimate the cost of $\OPT(\sigma_E)$ by accounting savings from migrations.
  By performing a swap of nodes $(u,v)$, $\OPT$ collocates $u$ with two nodes $u', u''$, and $v$ with two nodes $v'$, $v''$.
  This may allow to serve requests between $(u,u')$, $(u,u'')$, $(v,v')$ and $(v,v'')$ for free afterwards.
  As $\sigma_E$ consists of requests to unsaturated pairs, and it accounts only for external requests, there are at most $\alpha-1$ requests between each of these pairs.
  By performing a single migration that costs $\alpha$, $\OPT$ may avoid paying the remote serving costs for at most $4 (\alpha - 1)$ requests from $\sigma_E$.
  Thus, for serving $\sigma_E$, $\OPT$ pays at least $W \cdot \frac{\alpha}{4 (\alpha-1)}$.
  This gives us
  \begin{equation*}
    \OPT(\sigma_E) + \OPT(M)  \geq (|\sigma_E|-3(\alpha - 1)\cdot \ell) \cdot \frac{\alpha}{4 (\alpha-1)}
    \geq |\sigma_E| / 4 - 4 \alpha \cdot \ell.
  \end{equation*}
  From that, we obtain $|\sigma_E| \geq 4(\OPT(\sigma_E)+\OPT(M)) + 16\alpha \cdot \ell$.
  Let $E := \OPT(\sigma_E) + \OPT(M)$. Finally, we are ready to bound the competitive ratio
  \begin{equation*}
    \frac{\TAlg(\sigma)}{\OPT(\sigma)} \leq \frac{10\alpha \cdot \ell + |\sigma_E|}{(\alpha + \OPT(\sigma_E) + \OPT(M))/2} \leq \frac{52\alpha\cdot\ell + 8\cdot E}{\alpha + E} \leq 52 \ell = O(\ell).
  \end{equation*}
